---
title: "PhotoCold"
author: "Yunpeng Luo"
date: "March, 29, 2022"
output: html_document
---

## Description

**After exploring the general pattern of modelling GPP vs observational GPP, the next step to identify the specific period when the mismatch between modeled GPP and observed GPP in each site-->focused in the markdown file**

step1: tidy the table for GPP simulation vs GPP obs sites

step2: finding the way to separate out the model early simulation period

## step1: tidy the table
```{r}
library(kableExtra)
library("readxl")
table.path<-"../data-raw/raw_data/sites_info/"
load(file=paste0(table.path,"Available_sites_info.RDA"))
my_data<-df_sites_avai
my_data %>%
  kbl(caption = "Summary of sites with GPP estimation ") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

## step2: seprate the time period when model early estimation of GPP

### Part1: find the method to determine the period that with early GPP estimation

```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}
library(readr)
library(lubridate)
library(dplyr)
library(ggplot2)
library(tidyr)
library(cowplot)

#path to datasets
path<-"../data-raw/raw_data/Merged_data/"
load(paste0(path,"Merged_Flux_and_VIs.RDA"))
ddf<-df_merge;rm(df_merge)
#convert the format of date
#ddf$date<-strptime(ddf$date,format = "%d/%m/%Y")
# ddf$date<-as.Date(ddf$date,"%m/%d/%Y")

####
library(phenopix)
library(zoo)
#function: to smooth the time series
extract_smooth_y<-function(x,df){
  # x<-df_new$gpp_mod_FULL_f
  # df<-0.05
  x_sm<-SplineFit(x,df=df)
  y<-x_sm$fit$predicted
  return(y)
}

#function: to determine the green-up period
#using the threshold method:
Deter_greenup<-function(df,pos_max){
  # df<-df_subset
  # pos_max<-pos_max

  df_sel_sos<-df %>%
    dplyr::filter(doy<=pos_max)
  #1) calculate the amplitude of the time series
  #based on the 10% or 25% of amplitude:
  mn_sos<-min(df_sel_sos$gpp_mod_norm_sm,na.rm = T)
  mm<-max(df_sel_sos$gpp_mod_norm_sm,na.rm = T)
  amp_sos<-mm-mn_sos
  
  trs_10_sos<-mn_sos+0.1*amp_sos
  trs_25_sos<-mn_sos+0.25*amp_sos
   
  #2)determine the start of season(sos10, and sos25)
  #set the sos beyond Feburary
  N_length<-length(df_sel_sos$gpp_mod_norm_sm)
  sos10<-which.min(abs(as.numeric(df_sel_sos$gpp_mod_norm_sm[60:N_length] - trs_10_sos)))+59
  sos25<-which.min(abs(as.numeric(df_sel_sos$gpp_mod_norm_sm[60:N_length] - trs_25_sos)))+59
  #3)the end of the green-up period
  peak<-pos_max
  #4)additional:also determine eos10 and eos25
  df_sel_eos<-df %>%
    dplyr::filter(doy>=pos_max)
  mn_eos<-min(df_sel_eos$gpp_mod_norm_sm,na.rm = T)
  amp_eos<-mm-mn_eos
  #
  trs_10_eos<-mn_eos+0.1*amp_eos
  trs_25_eos<-mn_eos+0.25*amp_eos
  #
  eos10<-which.min(abs(as.numeric(df_sel_eos$gpp_mod_norm_sm - trs_10_eos)))
  eos25<-which.min(abs(as.numeric(df_sel_eos$gpp_mod_norm_sm - trs_25_eos)))
  #adjust the eos 10 and eos25
  eos25<-eos25+peak-1
  eos10<-eos10+peak-1
  #
  pos_agg<-data.frame(sos10=sos10,sos25=sos25,peak=peak,eos25=eos25,eos10=eos10)
  #plotting demonstration:
  # plot(df_subset$date,df$gpp_mod_norm,ylab = "Norm GPP",xlab = "",pch=".")
  # lines(df_subset$date,df$gpp_mod_roll20,ylab = "Norm GPP",xlab = "",lwd=1.2,col="red")
  # abline(h=c(trs_10_sos,trs_25_sos,trs_25_eos,trs_10_eos),col="red",lty=2)
  # abline(v=df_subset$date[c(sos10,sos25,eos25,eos10)],col="red")
  # text(df_subset$date[c(sos10,sos25,eos25,eos10)],0.8,labels = c("sos10","sos25","eos25","eos10"),col = "red",pos = c(2,4,2,4))
  # abline(v=df_subset$date[c(peak)],col="red")
  # text(df_subset$date[c(peak)],0.8,labels = c("peak"),col = "red",pos = c(4))
  return(pos_agg)
}
# 
##function to seprate the early GPP estimation period:
#after checking the data(data avaiablity, data quality) in all the sites(47 sites)-->at the end, I selecting 39 sites at end:

sep_data_indiffY_sepMismatch<-function(ddf,degf,Clim,PFT,site_name,avai_years){
  # ddf<-ddf
  # degf<-0.05  #degree of freedom for the spline smooth
  # Clim<-"Dfb"
  # PFT<-"MF"
  # site_name<-"US-Syv"
  # avai_years<-c(2002:2006,2012:2014)
  
  ##remember add dplyr:: for instance as sometimes two same name functions might conflict with each other
  df<-ddf %>%
  dplyr::filter(sitename==site_name) %>%
  dplyr::mutate(doy = yday(date), Year=year(date)) %>%
  dplyr::filter(Year %in% avai_years)
  #
  Years_unique<-unique(df$Year)
  
    #-------------------------------------------------------------------------------
    #Step1: normlization for all the years in one site
    #normalized the gpp_obs and gpp_mod using the gpp_max(95 percentile of gpp)
    #-------------------------------------------------------------------------------
    gpp_max_obs<-quantile(df$gpp_obs,0.95,na.rm = T)
    gpp_max_mod<-quantile(df$gpp_mod_FULL,0.95,na.rm = T)
    df$gpp_mod_norm<-df$gpp_mod_FULL/gpp_max_mod
    df$gpp_obs_norm<-df$gpp_obs/gpp_max_obs
    #first to gap-fill the ts to enable the ts smoothing
    #then smooth the time series of all the years uisng the spline(did not use at the moment)
    #hints:do not gap-fill gpp_obs if there are long gaps in the time sereis-->for biases calculation in step 4-->need to gapfill each year
    if(length(df$gpp_obs[!is.na(df$gpp_obs)])>30){
      df_new<-c()
      for(i in 1:length(Years_unique)){
      df_t<-df[df$Year==Years_unique[i],]
      df_t<-df_t %>%
          mutate(gpp_mod_norm_f=na.fill(gpp_mod_norm,c("extend")),gpp_obs_norm_f= na.fill(gpp_obs_norm,c(NA,"extend",NA))) %>%
      mutate(gpp_mod_norm_sm = extract_smooth_y(gpp_mod_norm_f,degf))
      df_new<-rbind(df_new,df_t)
      }
      #coercian gpp_obs to numeric as sometimes long NA makes the rbind wrong to convert to numeric format
      df_new$gpp_obs_norm_f<-as.numeric(df_new$gpp_obs_norm_f)
    }
    #
    N<-length(df$gpp_mod_FULL)
    #-------------------------------------------------------------------------------
    #Step 2:Determine the green-up period for each year(using spline smoothed values): 
    #followed analysis is based on the normlized "GPP_mod"time series(determine earlier sos)
    #-------------------------------------------------------------------------------
    #
    library(zoo)
    pos_diffYears<-c()
    #also subset data beyond the green-up period
    df_outgreenup<-c()
    df_final<-c()
    for(i in 1:length(Years_unique)){
    df_subset<-df_new[df_new$Year==Years_unique[i],]
    #spot t
    #calculate the rollmean 
    df_subset<-df_subset%>%
        dplyr::mutate(
               gpp_mod_roll5=rollapply(df_subset$gpp_mod_norm_f,5,mean,fill=NA,align="center"),
               gpp_mod_roll7=rollapply(df_subset$gpp_mod_norm_f,7,mean,fill=NA,align="center"),
               gpp_mod_roll10=rollapply(df_subset$gpp_mod_norm_f,10,mean,fill=NA,align="center"),
               gpp_mod_roll15=rollapply(df_subset$gpp_mod_norm_f,15,mean,fill=NA,align="center"),
               gpp_mod_roll20=rollapply(df_subset$gpp_mod_norm_f,20,mean,fill=NA,align="center"),
               gpp_obs_roll5=rollapply(df_subset$gpp_obs_norm_f,5,mean,fill=c(NA,"extend",NA),align="center"),
               gpp_obs_roll7=rollapply(df_subset$gpp_obs_norm_f,7,mean,fill=c(NA,"extend",NA),align="center"),
               gpp_obs_roll10=rollapply(df_subset$gpp_obs_norm_f,10,mean,fill=c(NA,"extend",NA),align="center"),
               gpp_obs_roll15=rollapply(df_subset$gpp_obs_norm_f,15,mean,fill=c(NA,"extend",NA),align="center"),
               gpp_obs_roll20=rollapply(df_subset$gpp_obs_norm_f,20,mean,fill=c(NA,"extend",NA),align="center"),
               temp_obs_roll20=rollapply(df_subset$temp_day_fluxnet2015,20,mean,fill=c(NA,"extend",NA),align="center")
               )
    # pos_sim_max<-match(max(df_subset$gpp_mod_roll20,na.rm = T),df_subset$gpp_mod_roll20)
    pos_sim_max<-match(max(df_subset$gpp_mod_norm_sm),df_subset$gpp_mod_norm_sm)
    pos_max<-pos_sim_max
    #finding out the start and end of the green-up period:
    pos_agg<-Deter_greenup(df_subset,pos_max)
    pos_diffYears<-rbind(pos_diffYears,pos_agg)
    #separate the data beyond greenup period:
    # pos_beyond<-c(1:c(pos_agg$sos10-1),c(c(pos_agg$peak+1):length(df_subset$date)))
    #pos_beyond<-c(pos_agg$peak+1):length(df_subset$date)
    pos_beyond<-c(1:c(pos_agg$sos10-1),c(c(pos_agg$eos10+1):length(df_subset$date)))
    t_outgreenup<-df_subset[pos_beyond,]
    df_outgreenup<-rbind(df_outgreenup,t_outgreenup)
    df_final<-rbind(df_final,df_subset)
    }
    rownames(pos_diffYears)<-Years_unique
    #-------------------------------------------------------------------------------
    #Step 3:rolling mean of GPPobs and GPPmod for data for all the years(moving windown:5,7,10, 15, 20days)
    #also for the data beyond green-up period-->moving to second step
    #-------------------------------------------------------------------------------
    # df_outgreenup<-df_outgreenup%>%
    #     mutate(gpp_mod_roll5=rollapply(df_outgreenup$gpp_mod_norm,5,mean,na.rm=T,fill=NA,align="center"),
    #            gpp_mod_roll7=rollapply(df_outgreenup$gpp_mod_norm,7,mean,na.rm=T,fill=NA,align="center"),
    #            gpp_mod_roll10=rollapply(df_outgreenup$gpp_mod_norm,10,mean,na.rm=T,fill=NA,align="center"),
    #            gpp_mod_roll15=rollapply(df_outgreenup$gpp_mod_norm,15,mean,na.rm=T,fill=NA,align="center"),
    #            gpp_mod_roll20=rollapply(df_outgreenup$gpp_mod_norm,20,mean,na.rm=T,fill=NA,align="center"),
    #            gpp_obs_roll5=rollapply(df_outgreenup$gpp_obs_norm,5,mean,na.rm=T,fill=NA,align="center"),
    #            gpp_obs_roll7=rollapply(df_outgreenup$gpp_obs_norm,7,mean,na.rm=T,fill=NA,align="center"),
    #            gpp_obs_roll10=rollapply(df_outgreenup$gpp_obs_norm,10,mean,na.rm=T,fill=NA,align="center"),
    #            gpp_obs_roll15=rollapply(df_outgreenup$gpp_obs_norm,15,mean,na.rm=T,fill=NA,align="center"),
    #            gpp_obs_roll20=rollapply(df_outgreenup$gpp_obs_norm,20,mean,na.rm=T,fill=NA,align="center")
    #            )
    #-------------------------------------------------------------------------------
    #Step 4:Fit the Guassian norm distribution for residuals beyond the green-up period
    #-------------------------------------------------------------------------------
    library(MASS)
    #calculate the residuals
    res.gpp<-data.frame(date=df_outgreenup$date,res=c(df_outgreenup$gpp_mod_roll20 - df_outgreenup$gpp_obs_roll20))
    res.gpp<-res.gpp[!is.na(res.gpp$res),]
    fit_res<-fitdistr(res.gpp$res,"normal")
    para <- fit_res$estimate
    # hist(res_gpp,probability = TRUE)
    # curve(dnorm(x, para[1], para[2]), col = 2, add = TRUE)
    mu<-mean(res.gpp$res,na.rm = T)
    p_density_res_outgreenup<-ggplot(res.gpp, aes(x=res))+
      geom_histogram(aes(y=..density..),binwidth = 0.01,position="identity", alpha=0.3,fill="white",col="green3",)+
      geom_density(col="forestgreen",size=1.05)+
      stat_function(fun = dnorm, args = list(mean = mean(res.gpp$res), sd = sd(res.gpp$res)),size=1.05,col="black")+
      geom_vline(xintercept=mu,linetype="dashed",size=1.05)+
      theme_minimal()
    #-------------------------------------------------------------------------------
    #step 5:determine the GPP overestimation("over_estim") within green-up and growing season(sos-eos)
    #and GPP overstimation happens less than 10 degree in the spring 
    # ("is_event_less10")
    #-------------------------------------------------------------------------------
    Sys.setenv(tz="UTC")
    df_diffYears<-c()
    for(i in 1:length(Years_unique)){
    df_subset<-df_final[df_final$Year==Years_unique[i],]
    #A.
    #a1.add one column to indicate the "greenup" 
    df_subset$greenup<-rep("no",length(df_subset$date))
    pos_agg<-pos_diffYears[i,]
    #green-up date=yes
    df_subset[c(df_subset$doy>=pos_agg$sos10) & c(df_subset$doy<=pos_agg$peak),]$greenup<-"yes"
    #a2.add one column to indicate the GS(growing season) 
    df_subset$GS<-rep("no",length(df_subset$date))
    #GS date=yes
    df_subset[c(df_subset$doy>=pos_agg$sos10) & c(df_subset$doy<=pos_agg$eos10),]$GS<-"yes"
    
    #B.
    #b1.add one column to indciate "is_event"
    #set the biases(gppmod-gppobs) are positive and bigger than 1.2sd as the "is_event"
    df_subset$gpp_res<-df_subset$gpp_mod_roll20-df_subset$gpp_obs_roll20
    #remove the NA
    # df_subset_rmNA<-df_subset[!is.na(df_subset$gpp_res),]
    thrs<-para[2]*3
    #"overestimation" in the growing season
    df_subset$over_estim<-rep("no",length(df_subset$date))
    #for the data is not equal to NA
    if(nrow(df_subset[c(df_subset$GS=="yes")&c(df_subset$gpp_res>thrs)&c(!is.na(df_subset$gpp_res)),])>0){
    df_subset[c(df_subset$GS=="yes")&c(df_subset$gpp_res>thrs)&c(!is.na(df_subset$gpp_res)),]$over_estim<-"yes"}
    #for the data is equal to NA-->not used any more
    # temp_subset<-df_subset[c(df_subset$GS=="yes")&c(df_subset$gpp_res>thrs)&c(is.na(df_subset$gpp_res)),]
    # if(length(temp_subset$date)>0){
    # df_subset[c(df_subset$GS=="yes")&c(df_subset$gpp_res>thrs)&c(is.na(df_subset$gpp_res)),]$over_estim<-rep(NA,length(temp_subset$date))
    # }
    #b2.add on column to indicate is_event-->GPP overestimation in the green-up period
    #"is_event"should be in the green-up period
    df_subset$is_event<-rep("no",length(df_subset$date))
    #for the data is not equal to NA
    if(nrow(df_subset[c(df_subset$greenup=="yes")&c(!is.na(df_subset$gpp_res)&c(df_subset$gpp_res>thrs)),])>0){
    df_subset[c(df_subset$greenup=="yes")&c(!is.na(df_subset$gpp_res)&c(df_subset$gpp_res>thrs)),]$is_event<-"yes"}
    #for the data is equal to NA
    if(length(df_subset[c(df_subset$greenup=="yes")&c(is.na(df_subset$gpp_res)),]$is_event)>0){
      df_subset[c(df_subset$greenup=="yes")&c(is.na(df_subset$gpp_res)),]$is_event<-"NA"
    }
    #b3. additional filter: only selecting the time period in the first 2/3 green-up for the determination-->
    greenup_subset<-subset(df_subset,greenup=="yes")
    sel_thres<-min(greenup_subset$doy)+round(c(max(greenup_subset$doy)-min(greenup_subset$doy))*2/3,0)
    df_subset[df_subset$doy>sel_thres,]$is_event<-"no"
    ############################
    #plotting
    #for the "GS"
    pos_GS<-df_subset$doy[which(df_subset$GS=="yes")]
    ##plotting
    # par(mfrow=c(2,1))
    # plot(df_subset$date,df_subset$temp_day_fluxnet2015,pch=1)
    # points(df_subset$date,df_subset$temp_obs_roll20,col="red")
    # abline(h=c(0,10,15),col="red")
    #
    # plot(df_subset$date,df_subset$gpp_mod_roll20,col="red",ylim=c(-0.1,1.2))
    # points(df_subset$date,df_subset$gpp_obs_roll20)
    # abline(v=df_subset$date[c(min(pos_GS),max(pos_GS))])
    #method:remove the positon of pos_overstimation when air temperature >10 (should be in the green-up period)
    pos_temp_less10<-df_subset$doy[which(c(df_subset$is_event=="yes") & c(df_subset$temp_obs_roll20<=10))]
    # abline(v=df_subset$date[c(min(pos_temp_less10),max(pos_temp_less10))],col="red")
    df_subset$is_event_less10<-df_subset$GS
    pos_rm<-setdiff(pos_GS,pos_temp_less10)
    df_subset$is_event_less10[pos_rm]<-rep("no",length(pos_rm))
    ##############################
    df_subset$date<-as.POSIXct(strptime(df_subset$date,format = "%Y-%m-%d"))
    #c.merge the data.frame
    df_diffYears<-rbind(df_diffYears,df_subset)
    }
    #-------------------------------------------------------------------------------
    #step 6:Evaluation "is_event"-->visualization and stats
    #-------------------------------------------------------------------------------
    #plotting+stats
    p_diffYears<-c()
    Pfalse_diffYears<-c()
    for(i in 1:length(Years_unique)){
    df_subset<-df_diffYears[df_diffYears$Year==Years_unique[i],]
    #a.stats:positive false%= days(gpp_mod underestimation for days flaged as is_event)/days(is_event)
    df_stats<-subset(df_subset,is_event=="yes"&!is.na(gpp_obs))
    df_stats$flag<-rep("overEsti",length(df_stats$date))
    for(k in 1:length(df_stats$date)){
      ifelse(df_stats$gpp_mod_FULL[k]-df_stats$gpp_obs[k]<0,df_stats$flag[k]<-"underEsti",df_stats$flag[k]<-df_stats$flag[k])
    }
    Pfalse<-round(c(length(which(df_stats$flag=="underEsti"))/length(df_stats$date)*100),1)
    Pfalse_diffYears<-rbind(Pfalse_diffYears,Pfalse)
    #b.plotting:demonstration the original value + moving average + dividing lines
    pos_agg<-pos_diffYears[i,]
    pos_overestim<-df_subset$doy[which(df_subset$over_estim=="yes")]
    pos_isevent<-df_subset$doy[which(df_subset$is_event=="yes")]
    pos_isevent_less10<-df_subset$doy[which(df_subset$is_event_less10=="yes")]
    
    rect.coord_GS=data.frame(x1=df_subset$date[pos_agg[,"sos10"]],x2=df_subset$date[pos_agg[,"eos10"]], y1=min(df_subset$gpp_mod_norm,na.rm = T)-0.05, y2=max(df_subset$gpp_mod_norm,na.rm = T)+0.02)
    rect.coord_isevent=data.frame(x1=df_subset$date[min(pos_isevent)],x2=df_subset$date[max(pos_isevent)], y1=min(df_subset$gpp_mod_norm,na.rm = T)-0.05, y2=max(df_subset$gpp_mod_norm,na.rm = T)+0.02)
    rect.coord_isevent_less10=data.frame(x1=df_subset$date[min(pos_isevent_less10)],x2=df_subset$date[max(pos_isevent_less10)], y1=min(df_subset$gpp_mod_norm,na.rm = T)-0.05, y2=max(df_subset$gpp_mod_norm,na.rm = T)+0.02)
#
  
  gg_plot<-ggplot() + 
      geom_point(data=df_subset,aes(x=date,y = gpp_mod_norm),col=adjustcolor("tomato",0.5),pch=1)+
      geom_line(data=df_subset,aes(x=date,y = gpp_mod_roll20,col="modelled"),lwd=1.2)+
      geom_point(data=df_subset,aes(x=date,y = gpp_obs_norm),col=adjustcolor("black",0.5),pch=1)+
      geom_line(data=df_subset,aes(x=date,y = gpp_obs_roll20,col="observed"),lwd=1.2)+
      geom_vline(xintercept = df_subset$date[pos_agg[,"sos10"]],col="forestgreen",lty=2,lwd=1.2)+
      geom_vline(xintercept = df_subset$date[pos_agg[,"peak"]],col="forestgreen",lty=2,lwd=1.2)+
      scale_color_manual("",values = c("modelled"="red","observed"="black")) +
      labs(title = paste0(Clim,"-",PFT,"-",site_name,":",Years_unique[i]), x = "", y = "norm GPP" )+  #(g C m-2 d-1 )
  geom_rect(data=rect.coord_GS,mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill="green3",alpha=0.1)+
  geom_vline(xintercept = df_subset[df_subset$over_estim=="yes",]$date,col=adjustcolor("steelblue2",0.3))+
  geom_rect(data=rect.coord_isevent,mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill="blue",alpha=0.3)+
  # geom_rect(data=rect.coord_isevent_less10,mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill="orange",alpha=0.5)+
  theme_classic()+
  theme(legend.position = c(0.15,0.9),legend.background = element_blank())
  
  ## merge the plot
  ifelse(i==1,gg_plot<-gg_plot+theme(),gg_plot<-gg_plot+theme(legend.position = "none"))
  # plot(gg_plot)
  p_diffYears[[i]]<-gg_plot
    }
  Pfalse_diffYears<-as.data.frame(Pfalse_diffYears)
  names(Pfalse_diffYears)<-"Pflase";rownames(Pfalse_diffYears)<-Years_unique
    #-------------------------------------------------------------------------------
    #step 7:Summary
    #-------------------------------------------------------------------------------
  df_agg<-c()
  df_agg$pos_agg<-pos_diffYears
  df_agg$df_agg<-df_diffYears
  df_agg$p_den_outgreenup<-p_density_res_outgreenup
  df_agg$Pflase<-Pfalse_diffYears
  df_agg$p_isevent<-p_diffYears
  return(df_agg)
}
```

### Part 2: check all the sites (47 sites-->used 39 sites at the end)
```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}
#test
# df_andPlot_Cfb_DBF<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","DBF","DE-Hai",c(2002:2012))
# length(df_andPlot_Dfc_GRA$p_isevent)
# p_diffYears<-df_andPlot_Cfb_DBF$p_isevent
# p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
#           p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
#           p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
#           p_diffYears[[10]],p_diffYears[[11]],
#           labels = "auto",ncol=3,label_size = 12,align = "hv")
# plot(p_merge)
```
**(1) For Cfa:both for DBF, MF, and ENF sites(5 sites-->used 5 sites at the end)**
```{r}
my_data_Cfa<-my_data[my_data$koeppen_code=="Cfa",]
```
- Cfa-DBF (3 sites)
```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}
#IT-Col-->select available complete-spring years and proper summer peak year:2001,2005,2007:2011,2013:2014
site_name<-"IT-Col"
df<-ddf %>%
  dplyr::filter(sitename==site_name)
df_andPlot_Cfa_DBF1<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfa","DBF",site_name,c(2001,2005,2007:2011,2013:2014))
length(df_andPlot_Cfa_DBF1$p_isevent)
p_diffYears<-df_andPlot_Cfa_DBF1$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#IT-PT1-->select available complete-spring years and proper summer peak years:2003:2004
site_name<-"IT-PT1"
df<-ddf %>%
  dplyr::filter(sitename==site_name)
df_andPlot_Cfa_DBF2<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfa","DBF",site_name,c(2003:2004))
length(df_andPlot_Cfa_DBF2$p_isevent)
p_diffYears<-df_andPlot_Cfa_DBF2$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#US-MMS-->successful-->change Dfa-->Cfa compared to my former code
df_andPlot_Cfa_DBF3<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfa","DBF","US-MMS",c(2000:2014))
length(df_andPlot_Cfa_DBF3$p_isevent)
p_diffYears<-df_andPlot_Cfa_DBF3$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],p_diffYears[[14]],p_diffYears[[15]],        
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)
#
temp.save.path="D:/CES/CES_Group_meeting/PhotoCold_Project/20220523_WSL_poster_prep/fig/"
p_temp<-p_diffYears[[12]]+
  theme(axis.text = element_text(size=20,angle = 12.5),
        axis.title = element_text(size=26),
        legend.text = element_text(size=26),
        legend.position = c(0.15,0.9))+
  ylab("Norm GPP")
ggsave(p_temp,filename = paste0(temp.save.path,"GPP_overestimation.png"),width = 10,height = 8)
```
- Cfa-MF (1 site)
```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}
#JP-SMF-->successful
df_andPlot_Cfa_MF<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfa","MF","JP-SMF",c(2003:2006))
length(df_andPlot_Cfa_MF$p_isevent)
p_diffYears<-df_andPlot_Cfa_MF$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)
```
- Cfa-ENF (1 site)
```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}
#CN-Qia-->successful
df_andPlot_Cfa_ENF<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfa","ENF","CN-Qia",c(2003:2006))
length(df_andPlot_Cfa_ENF$p_isevent)
p_diffYears<-df_andPlot_Cfa_ENF$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)
```

**(2) For Cfb: for DBF,MF and ENF (14 sites-->used 12 sites at the end)**
```{r}
my_data_Cfb<-my_data[my_data$koeppen_code=="Cfb",]
```
- Cfb-DBF (4 sites)
```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}
#DE-Hai-->successful
site_name<-"DE-Hai"
df_andPlot_Cfb_DBF1<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","DBF",site_name,c(2000:2012))
length(df_andPlot_Cfb_DBF1$p_isevent)
p_diffYears<-df_andPlot_Cfb_DBF1$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#DK-Sor-->successful
site_name<-"DK-Sor"
df_andPlot_Cfb_DBF2<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","DBF",site_name,c(2000:2003,2005:2013))
length(df_andPlot_Cfb_DBF2$p_isevent)
p_diffYears<-df_andPlot_Cfb_DBF2$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],       
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#FR-Fon-->successful
site_name<-"FR-Fon"
df_andPlot_Cfb_DBF3<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","DBF",site_name,c(2006:2013))
length(df_andPlot_Cfb_DBF3$p_isevent)
p_diffYears<-df_andPlot_Cfb_DBF3$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#IT-Isp
site_name<-"IT-Isp"
df<-ddf %>%
  dplyr::filter(sitename==site_name)
df_andPlot_Cfb_DBF4<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","DBF",site_name,c(2013:2014))
length(df_andPlot_Cfb_DBF4$p_isevent)
p_diffYears<-df_andPlot_Cfb_DBF4$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)
```
- Cfb-MF (3 sites-->2 sites used at the end)
```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}
#BE-Bra --> there are no gpp_obs data-->hence not use this site
site_name<-"BE-Bra"
# df<-ddf %>%
#   dplyr::filter(sitename==site_name)
# df_andPlot_Cfb_MF<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","MF",site_name,c(1996:2014))
# length(df_andPlot_Cfb_MF$p_isevent)
# p_diffYears<-df_andPlot_Cfb_MF$p_isevent
# p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
#           p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
#           p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
#           p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
#           p_diffYears[[13]],p_diffYears[[14]],p_diffYears[[15]],
#           labels = "auto",ncol=3,label_size = 12,align = "hv")
# plot(p_merge)

#BE-Vie
site_name<-"BE-Vie"
df_andPlot_Cfb_MF1<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","MF",site_name,c(2000:2014))
length(df_andPlot_Cfb_MF1$p_isevent)
p_diffYears<-df_andPlot_Cfb_MF1$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],p_diffYears[[14]],p_diffYears[[15]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#CH-Lae
site_name<-"CH-Lae"
df_andPlot_Cfb_MF2<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","MF",site_name,c(2005:2014))
length(df_andPlot_Cfb_MF2$p_isevent)
p_diffYears<-df_andPlot_Cfb_MF2$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)
```
- Cfb-ENF (7 sites-->6 sites used at the end)
```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}
#DE-Lkb
site_name<-"DE-Lkb"
df_andPlot_Cfb_ENF1<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","ENF",site_name,c(2010:2013))
length(df_andPlot_Cfb_ENF1$p_isevent)
p_diffYears<-df_andPlot_Cfb_ENF1$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
print(p_merge)

#DE-Obe
site_name<-"DE-Obe"
df_andPlot_Cfb_ENF2<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","ENF",site_name,c(2008:2014))
length(df_andPlot_Cfb_ENF2$p_isevent)
p_diffYears<-df_andPlot_Cfb_ENF2$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#DE-Tha
site_name<-"DE-Tha"
df_andPlot_Cfb_ENF3<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","ENF",site_name,c(2000:2014))
length(df_andPlot_Cfb_ENF3$p_isevent)
p_diffYears<-df_andPlot_Cfb_ENF3$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],p_diffYears[[14]],p_diffYears[[15]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#FR-LBr
site_name<-"FR-LBr"
df_andPlot_Cfb_ENF4<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","ENF",site_name,c(2001,2004:2008))
length(df_andPlot_Cfb_ENF4$p_isevent)
p_diffYears<-df_andPlot_Cfb_ENF4$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#IT-La2 -->only have one complete year, hence do not use
site_name<-"IT-La2"
# df<-ddf %>%
#   dplyr::filter(sitename==site_name)
# df_andPlot_Cfb_ENF<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","ENF",site_name,c(2001,2004:2008))
# length(df_andPlot_Cfb_ENF$p_isevent)
# p_diffYears<-df_andPlot_Cfb_ENF$p_isevent
# p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
#           p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
#           labels = "auto",ncol=3,label_size = 12,align = "hv")
# plot(p_merge)

#IT-Lav-->successful
site_name<-"IT-Lav"
df_andPlot_Cfb_ENF5<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","ENF",site_name,c(2003:2014))
length(df_andPlot_Cfb_ENF5$p_isevent)
p_diffYears<-df_andPlot_Cfb_ENF5$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],        
          labels = "auto",ncol=3,label_size = 12,align = "hv")
print(p_merge)

#NL-Loo
site_name<-"NL-Loo"
df_andPlot_Cfb_ENF6<-sep_data_indiffY_sepMismatch(ddf,0.05,"Cfb","ENF",site_name,c(2000:2013))
length(df_andPlot_Cfb_ENF6$p_isevent)
p_diffYears<-df_andPlot_Cfb_ENF6$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],p_diffYears[[14]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)
```

**(3) For Cfc: 0 sites**
```{r}
my_data_Cfc<-my_data[my_data$koeppen_code=="Cfc",]
```

**(4) For Dfa: 0 sites **
```{r}
my_data_Dfa<-my_data[my_data$koeppen_code=="Dfa",]
```

**(5) For Dfb: for DBF, MF and ENF (14 sites-->used 10 sites in the end) **
```{r}
my_data_Dfb<-my_data[my_data$koeppen_code=="Dfb",]
```
- Dfb-DBF (6 site-->used 5 sites in the end)
```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}
#JP-MBF
site_name<-"JP-MBF"
df<-ddf %>%
  dplyr::filter(sitename==site_name)
df_andPlot_Dfb_DBF1<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfb","DBF",site_name,c(2004:2005))
length(df_andPlot_Dfb_DBF1$p_isevent)
p_diffYears<-df_andPlot_Dfb_DBF1$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#US-UMB
site_name<-"US-UMB"
df_andPlot_Dfb_DBF2<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfb","DBF",site_name,c(2000:2014))
length(df_andPlot_Dfb_DBF2$p_isevent)
p_diffYears<-df_andPlot_Dfb_DBF2$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],p_diffYears[[14]],p_diffYears[[15]],        
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#US-UMd
site_name<-"US-UMd"
df_andPlot_Dfb_DBF3<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfb","DBF",site_name,c(2008:2014))
length(df_andPlot_Dfb_DBF3$p_isevent)
p_diffYears<-df_andPlot_Dfb_DBF3$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],      
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#US-Ha1-->successful
site_name<-"US-Ha1"
df_andPlot_Dfb_DBF4<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfb","DBF",site_name,c(2000:2012))
length(df_andPlot_Dfb_DBF4$p_isevent)
p_diffYears<-df_andPlot_Dfb_DBF4$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#US-Wcr
site_name<-"US-WCr"
df_andPlot_Dfb_DBF5<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfb","DBF",site_name,c(2000:2006,2011:2014))
length(df_andPlot_Dfb_DBF5$p_isevent)
p_diffYears<-df_andPlot_Dfb_DBF5$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#US-Wi3-->lack early spring observation
site_name<-"US-Wi3"
df<-ddf %>%
  dplyr::filter(sitename==site_name)
# df_andPlot<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfb","DBF","US-WCr",c(2002,2004))
# length(df_andPlot$p_agg)
# p_diffYears<-df_andPlot$p_agg
# p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],
#           labels = "auto",ncol=3,label_size = 12,align = "hv")
# plot(p_merge)

```
- Dfb-MF (2 sites-->used 2 sites)
```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}
#US-PFa-->successful
site_name<-"US-PFa"
df_andPlot_Dfb_MF1<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfb","MF",site_name,c(2000:2004,2006:2014))
length(df_andPlot_Dfb_MF1$p_isevent)
p_diffYears<-df_andPlot_Dfb_MF1$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],p_diffYears[[14]],        
          labels = "auto",ncol=3,label_size = 12,align = "hv")
print(p_merge)

#US-Syv
site_name<-"US-Syv"
df_andPlot_Dfb_MF2<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfb","MF",site_name,c(2002:2006,2012:2014))
length(df_andPlot_Dfb_MF2$p_isevent)
p_diffYears<-df_andPlot_Dfb_MF2$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)
```
- Dfb-ENF (6 sites-->used 3 sites in the end)
```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}

#CZ-BK1-->successful
site_name<-"CZ-BK1"
df_andPlot_Dfb_ENF1<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfb","ENF",site_name,c(2004:2008))
length(df_andPlot_Dfb_ENF1$p_isevent)
p_diffYears<-df_andPlot_Dfb_ENF1$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
print(p_merge)

#RU-Fyo-->successful
site_name<-"RU-Fyo"
df_andPlot_Dfb_ENF2<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfb","ENF",site_name,c(2000:2001,2003:2014))
length(df_andPlot_Dfb_ENF2$p_isevent)
p_diffYears<-df_andPlot_Dfb_ENF2$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],p_diffYears[[14]],        
          labels = "auto",ncol=3,label_size = 12,align = "hv")
print(p_merge)

#US-GLE-->successful
site_name<-"US-GLE"
df_andPlot_Dfb_ENF3<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2006:2014))
length(df_andPlot_Dfb_ENF3$p_isevent)
p_diffYears<-df_andPlot_Dfb_ENF3$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
print(p_merge)

#US-Wi0-->do not use as one year and lack spring data
site_name<-"US-Wi0"
# df<-ddf %>%
#   dplyr::filter(sitename==site_name)
# df_andPlot_Dfc_ENF<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2006:2014))
# length(df_andPlot_Dfc_ENF$p_isevent)
# p_diffYears<-df_andPlot_Dfc_ENF$p_isevent
# p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
#           p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
#           p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
#           labels = "auto",ncol=3,label_size = 12,align = "hv")
# print(p_merge)

#US-Wi4-->do not use as lack spring data
site_name<-"US-Wi4"
# df<-ddf %>%
#   dplyr::filter(sitename==site_name)
# df_andPlot_Dfc_ENF<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2002:2005))
# length(df_andPlot_Dfc_ENF$p_isevent)
# p_diffYears<-df_andPlot_Dfc_ENF$p_isevent
# p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
#           p_diffYears[[4]],
#           labels = "auto",ncol=3,label_size = 12,align = "hv")
# print(p_merge)

#US-Wi9-->do not use as lack spring data
site_name<-"US-Wi9"
# df<-ddf %>%
#   dplyr::filter(sitename==site_name)
# df_andPlot_Dfc_ENF<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2004:2005))
# length(df_andPlot_Dfc_ENF$p_isevent)
# p_diffYears<-df_andPlot_Dfc_ENF$p_isevent
# p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
#           p_diffYears[[4]],
#           labels = "auto",ncol=3,label_size = 12,align = "hv")
# print(p_merge)
```

**(6) For Dfc:for ENF sites (14 sites--> used 12 sites at the end)**
```{r}
my_data_Dfc<-my_data[my_data$koeppen_code=="Dfc",]
```
- Dfc-ENF (14 sites-->at the end used 12 sites)
```{r echo = FALSE, message = FALSE, warning = FALSE,fig.height=10,fig.width=10}
#CA-Man
site_name<-"CA-Man"
df_andPlot_Dfc_ENF1<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2000:2003,2007:2008))
length(df_andPlot_Dfc_ENF1$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF1$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#CA-NS1-->successful
site_name<-"CA-NS1"
df_andPlot_Dfc_ENF2<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2003:2005))
length(df_andPlot_Dfc_ENF2$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF2$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#CA-NS2-->selected the years with early spring
site_name<-"CA-NS2"
df<-ddf %>%
  dplyr::filter(sitename==site_name)
df_andPlot_Dfc_ENF3<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2002:2004))
length(df_andPlot_Dfc_ENF3$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF3$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#CA-NS3-->succesful
site_name<-"CA-NS3"
df_andPlot_Dfc_ENF4<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2002:2005))
length(df_andPlot_Dfc_ENF4$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF4$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
print(p_merge)

#CA-NS4
site_name<-"CA-NS4"
df<-ddf %>%
  dplyr::filter(sitename==site_name)
df_andPlot_Dfc_ENF5<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2003,2005))
length(df_andPlot_Dfc_ENF5$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF5$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
print(p_merge)

#CA-NS5
site_name<-"CA-NS5"
df<-ddf %>%
  dplyr::filter(sitename==site_name)
df_andPlot_Dfc_ENF6<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2002:2005))
length(df_andPlot_Dfc_ENF6$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF6$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
print(p_merge)

#CA-Qfo
site_name<-"CA-Qfo"
df_andPlot_Dfc_ENF7<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2004:2010))
length(df_andPlot_Dfc_ENF7$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF7$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#CA-SF1-->do not use as no early Spring data 
site_name<-"CA-SF1"
# df<-ddf %>%
#   dplyr::filter(sitename==site_name)
# df_andPlot_Dfc_ENF<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2004:2006))
# length(df_andPlot_Dfc_ENF$p_isevent)
# p_diffYears<-df_andPlot_Dfc_ENF$p_isevent
# p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
#           p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
#           p_diffYears[[7]],
#           labels = "auto",ncol=3,label_size = 12,align = "hv")
# plot(p_merge)

#CA-SF2-->do not use as no early Spring data
site_name<-"CA-SF2"
# df<-ddf %>%
#   dplyr::filter(sitename==site_name)
# df_andPlot_Dfc_ENF<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2004:2006))
# length(df_andPlot_Dfc_ENF$p_isevent)
# p_diffYears<-df_andPlot_Dfc_ENF$p_isevent
# p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
#           p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
#           p_diffYears[[7]],
#           labels = "auto",ncol=3,label_size = 12,align = "hv")
# plot(p_merge)

#FI-Hyy
site_name<-"FI-Hyy"
df_andPlot_Dfc_ENF8<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2000:2014))
length(df_andPlot_Dfc_ENF8$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF8$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],p_diffYears[[14]],p_diffYears[[15]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

##IT-Ren
site_name<-"IT-Ren"
df_andPlot_Dfc_ENF9<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2002:2003,2005:2013))
length(df_andPlot_Dfc_ENF9$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF9$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#US-GBT
site_name<-"US-GBT"
df<-ddf %>%
  dplyr::filter(sitename==site_name)
df_andPlot_Dfc_ENF10<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2002:2003))
length(df_andPlot_Dfc_ENF10$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF10$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
print(p_merge)

#US-NR1-->successful
site_name<-"US-NR1"
df_andPlot_Dfc_ENF11<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF",site_name,c(2000:2014))
length(df_andPlot_Dfc_ENF11$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF11$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],p_diffYears[[3]],
          p_diffYears[[4]],p_diffYears[[5]],p_diffYears[[6]],
          p_diffYears[[7]],p_diffYears[[8]],p_diffYears[[9]],
          p_diffYears[[10]],p_diffYears[[11]],p_diffYears[[12]],
          p_diffYears[[13]],p_diffYears[[14]],p_diffYears[[15]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

#US-Prr-->select the early Spring data
site_name<-"US-Prr"
df_andPlot_Dfc_ENF12<-sep_data_indiffY_sepMismatch(ddf,0.05,"Dfc","ENF","US-Prr",c(2011:2012))
length(df_andPlot_Dfc_ENF12$p_isevent)
p_diffYears<-df_andPlot_Dfc_ENF12$p_isevent
p_merge<-plot_grid(p_diffYears[[1]],p_diffYears[[2]],
          labels = "auto",ncol=3,label_size = 12,align = "hv")
plot(p_merge)

```

**(7) For Dfd:for ENF sites(0 sites)**
```{r}
my_data_Dfd<-my_data[my_data$koeppen_code=="Dfd",]
```

##updates: 11-19
## step3: save the data that label with "is_event"
```{r echo = FALSE, message = FALSE, warning = FALSE}
#put the results together
#do not add Dfb_DBF4
df_all<-list(df_andPlot_Cfa_DBF1,df_andPlot_Cfa_DBF2,df_andPlot_Cfa_DBF3,
             df_andPlot_Cfa_MF,df_andPlot_Cfa_ENF,  #5
    df_andPlot_Cfb_DBF1,df_andPlot_Cfb_DBF2,df_andPlot_Cfb_DBF3,df_andPlot_Cfb_DBF4,
    df_andPlot_Cfb_MF1,df_andPlot_Cfb_MF2,
    df_andPlot_Cfb_ENF1,df_andPlot_Cfb_ENF2,df_andPlot_Cfb_ENF3,
    df_andPlot_Cfb_ENF4,df_andPlot_Cfb_ENF5,df_andPlot_Cfb_ENF6, #17
    df_andPlot_Dfb_DBF1,df_andPlot_Dfb_DBF2,df_andPlot_Dfb_DBF3,
    df_andPlot_Dfb_DBF4,df_andPlot_Dfb_DBF5,
    df_andPlot_Dfb_MF1,df_andPlot_Dfb_MF2,
    df_andPlot_Dfb_ENF1,df_andPlot_Dfb_ENF2,df_andPlot_Dfb_ENF3,#27
    df_andPlot_Dfc_ENF1,df_andPlot_Dfc_ENF2,df_andPlot_Dfc_ENF3,
    df_andPlot_Dfc_ENF4,df_andPlot_Dfc_ENF5,df_andPlot_Dfc_ENF6,
    df_andPlot_Dfc_ENF7,df_andPlot_Dfc_ENF8,df_andPlot_Dfc_ENF9,
    df_andPlot_Dfc_ENF10,df_andPlot_Dfc_ENF11,df_andPlot_Dfc_ENF12 #39
    )

names(df_all)<-c("IT-Cor","IT-PT1","US-MMS",
                 "JP-SMF","CN-Qia", #5
                 "DE-Hai","DK-Sor","FR-Fon","IT-Isp",
                 "BE-Vie","CH-Lae",
                 "DE-Lkb","DE-Obe","DE-Tha",
                 "FR-LBr","IT-Lav","NL-Loo", #17
                 "JP-MBF","US-UMB","US-UMd",
                 "US-Ha1","US-WCr",
                 "US-PFa","US-Syv",
                 "CZ-Bk1","RU-Fyo","US-GLE",#27
                 "CA-Man","CA-NS1","US-NS2", 
                 "CA-NS3","CA-NS4","CA-NS5",
                 "CA-Qfo","FI-Hyy","IT-Ren",
                 "US-GBT","US-NR1","US-Prr")#39
ddf_labeled<-c()
for(i in 1:length(df_all)){
  ddf_labeled<-rbind(ddf_labeled,df_all[[i]]$df_agg)
}
#save the data:
save.path<-"../data/data_used/"
save(ddf_labeled,file=paste0(save.path,"ddf_labeled_norm_trs_newmethod_all_overestimation_Fluxnet2015_sites.RDA"))
# save(df_all,file=paste0(save.path,"df_all_results/df_all_norm_trs_newmethod_all_overestimation_Fluxnet2015_sites.RDA"))
```


## Summary

### steps to determine the "is_event" period

    
    **Step1: normlization for all the years in one site**
     
    #normalized the gpp_obs and gpp_mod using the gpp_max(95 percentile of gpp)
    
    
    **Step 2:Determine the green-up period for each year(using spline smoothed values):** 
    
    #followed analysis is based on the normlized "GPP_mod"time series(determine earlier sos)
    
    - using the normalized GPP_mod to determine sos,eos and peak of the time series (using the threshold, percentile 10 of amplitude, to determine the sos and eos in this study). We selected the GPP_mod to determine the phenophases as genearlly we can get earlier sos compared to GPP_obs--> we can have larger analysis period
    - update in Aug,31,2011-->limit the sos late than Feburary(Doy:60)-->in order to remove some unrelastic sos
    
    **Step 3:rolling mean of GPPobs and GPPmod for data for all the years(moving windown:5,7,10, 15, 20days)**
    
    **also for the data beyond green-up period--> the code of this steps moves to second step**
    
    - at the end, I select the 20 days windows for the rolling mean
    
    
    **Step 4:Fit the Guassian norm distribution for residuals beyond the green-up period**
    
    - The reason to conduct this are: we assume in general the P-model assume the GPP well outside the green-up period (compared to the observation data). 
    
    - But in practise, the model performance is not always good beyond the green-up period-->I tested three data range:
    
      a. [peak,265/366]
      
      b. DoY[1, sos]& DOY[peak,365/366]
      
      c. [1,sos] & [eos,365/366]
      
    I found the using the data range c, the distrbution of biase (GPP_mod - GPP_obs) is more close to the norm distribution, hence at end of I used the data range c to build the distribution.
    
    
    **step 5:determine the "is_event" within green-up period**
    
      - After some time of consideration, I took following crition to determine the "is_event":
      
        1) during the green-up period (sos,peak)-->the data with GPP biases bigger than 3 SD are classified as the "GPP overestimation points"
        2) For "GPP overestimation points" --> only regard the data points in the first 2/3 green-up period as the "is_event"
        
        3) For "is_event points", thoses are air temparture is less than 10 degrees will be classified as the "is_event_less10". I selected 10 degree as the crition by referring to the paper Duffy et al., 2021 and many papers which demonstrate the temperature response curve normally from 10 degree (for instance: Lin et al., 2012)
      
        References:
        
        Duffy et al., 2021:https://advances.sciencemag.org/content/7/3/eaay1052
        
        Lin et al., 2012:https://academic.oup.com/treephys/article/32/2/219/1657108
        
      
    **step 6:Evaluation "is_event"-->visualization and stats**
    
     - two ways to evaluate if "is_event" is properly determined:
     
      1) visulization
      
      2) stats:
      $$
      Pfalse = /frac{days(real_{(is-event)})}{days(flagged_{(is-event)})} 
      $$